% Appendix
\section*{Appendices}

    \subsection*{A — Glossary of Terms and Acronyms}
        \addcontentsline{toc}{subsection}{A. Glossary of Terms and Acronyms}
        \begin{itemize}
            \item \textbf{UAV} — Unmanned Aerial Vehicle; an aircraft without a human pilot onboard, commonly referred to as a drone.

            \item \textbf{DRL} — Deep Reinforcement Learning; a class of machine learning algorithms combining deep learning and reinforcement learning principles to learn policies in high-dimensional spaces.

            \item \textbf{RL} — Reinforcement Learning; a machine learning paradigm in which agents learn to take actions in an environment to maximize cumulative reward.

            \item \textbf{PPO} — Proximal Policy Optimization; a state-of-the-art policy gradient algorithm used in reinforcement learning for training stable and efficient stochastic policies.

            \item \textbf{IFF} — Identification Friend or Foe; a method for automatically distinguishing allied units from enemies, critical for avoiding fratricide in combat scenarios.

            \item \textbf{GNN} — Graph Neural Network; a type of neural network architecture particularly suited for learning over structured graph data, often applied in multi-agent systems.

            \item \textbf{PID} — Proportional-Integral-Derivative controller; a classical control algorithm widely used in robotics and flight control systems.

            \item \textbf{P2P} — Peer-to-Peer; a decentralized communication model in which nodes (e.g., drones) share information directly without a central coordinator.

            \item \textbf{ESP32} — A low-cost, low-power microcontroller with built-in Wi-Fi and Bluetooth, commonly used in lightweight embedded UAV systems.

            \item \textbf{GUI} — Graphical User Interface; a visual interface for interacting with a system, in this context referring to the visual output of the PyBullet simulator.

            \item \textbf{CNN} — Convolutional Neural Network; a deep learning architecture mainly used for processing grid-like data such as images, potentially applicable to onboard visual recognition.

            \item \textbf{RLlib} — A scalable library for reinforcement learning built on Ray, commonly used for distributed training of agents.

            \item \textbf{SB3} — Stable-Baselines3; a widely used Python library for reinforcement learning built on top of PyTorch, offering standard implementations of DRL algorithms.

            \item \textbf{LAWS} — Lethal Autonomous Weapon Systems; weapon systems that can select and engage targets without human intervention, a subject of active ethical and legal debate.

            \item \textbf{LOAC} — Law of Armed Conflict; the body of international law regulating the conduct of armed hostilities, including principles such as distinction, proportionality, and necessity.

            \item \textbf{CNN-based IFF} — An IFF system based on convolutional neural networks, used to classify visual or sensor data as friend or foe.

            \item \textbf{Sim-to-Real} — A methodology where models trained in simulation are transferred to real-world systems with minimal adjustment.

            \item \textbf{Autopilot} — A control system that allows a vehicle to operate independently by following a pre-programmed or dynamically generated trajectory.

            \item \textbf{Swarm Intelligence} — The collective behavior of decentralized, self-organized systems, often inspired by natural phenomena like bird flocks or ant colonies.

            \item \textbf{Black-box Model} — A model whose internal workings are not transparent or easily interpretable, typically referring to deep neural networks.

            \item \textbf{Reward Shaping} — A reinforcement learning technique where intermediate rewards are introduced to accelerate and guide learning.

            \item \textbf{Kill Switch} — A hardware or software mechanism that allows emergency interruption or disabling of an autonomous system.
        \end{itemize}