\documentclass[twocolumn]{NobArticle}
\runninghead{Autonomous Drone Swarms with IFF and Targeting}
\footertext{\textit{Rolando L. Innamorati} (2025)}

\title{Decentralized Learning for Autonomous Kamikaze Drone Swarms with Integrated IFF and Target Engagement in Adversarial Environments}

\author{
    Rolando Licia Innamorati\textsuperscript{1,2}
}

\date{
    \textsuperscript{\textbf{1}}
    Delta Service Srl
    \textsuperscript{\textbf{2}}
    Università degli Studi dell'Aquila
}

\renewcommand{\maketitlehookd}{
\begin{abstract}
    \noindent We present an integrated and decentralized learning framework for autonomous kamikaze drones equipped with friend-or-foe (IFF) classification, onboard autopilot, and swarm-level coordination. Designed for deployment on resource-constrained hardware, our system leverages end-to-end deep reinforcement learning (DRL) to train each drone to execute high-speed, collision-aware attack trajectories against mobile adversarial targets, while explicitly avoiding friendly units. Each agent operates using only local observations—including its own motion state, relative positions of nearby agents, and IFF-informed target classification—without any centralized control or global state synchronization.

    Our simulation environment models sacrificial drone behavior: upon successful impact, the agent is removed from the mission space. We define a composite reward function that promotes successful hits, penalizes collisions with teammates or friendly entities, and encourages cooperative interception patterns. Experimental results show that intelligent group behaviors such as wave-based attacks, multi-angle encirclement, and selective avoidance of non-hostile targets emerge naturally from decentralized training. This demonstrates the feasibility of building self-organizing kamikaze swarms capable of friend-aware target engagement using lightweight onboard computation, laying the groundwork for practical implementation on minimalist UAV platforms.
    \medskip

    \small{\textbf{Index Terms:} Autonomous UAVs, Kamikaze Drone, Deep Reinforcement Learning, Friend-or-Foe Recognition, Swarm Warfare.}
\end{abstract}
}

\begin{document}

\small
\maketitle

\input{Sections/01-Introduction}
\input{Sections/02-Problem-Definition}
\input{Sections/03-Methodology}
\input{Sections/04-Experimental-Evaluation}
\input{Sections/05-Related-Works}
\input{Sections/06-Ethical}
\input{Sections/07-Conclusion}

\input{Sections/Appendix}

\printbibliography

\end{document}
